Linear instability underlying synchronous waving of marine grass in flow

### 2014-09-04 Paper/grass.tex
abstract update sep 4

%The spontaneous waving of marine grass is thought to be due to a Kelvin-Helmholtz instability resulting from an inflection point near the canopy top in the flow profile.
We study the mechanism behind Mo-nami, a phenomenon associated with the synchronous waving of marine grass. Linear stability analysis of a mathematical model incorporating grass drag as a continuum field has been 
carried out. Our analysis predicts a critical threshold condition for flow instability leading to Mo-nami and associated waving frequency
which compares well with experimental observations. Further analysis predicts existence of two distinct mode of instability.
One of these mode has many characteristics similar to the Kelvin-Helmholtz instability where shear layer formed near grass tip due to drag discontinuity plays a critical role, we termed this as ``Mode 1''. 
The other mode can be interpreted as instability of 
inviscid flow through a grass bed where shear layer doesn't play an important role, we refer this as ``Mode 2''. In the limit of dense grass bed these two modes can be
distinguished. For the parameter regime typical of marine grass beds, the two modes merge and are indistinguishable.

>>>>

%The spontaneous waving of marine grass is thought to be due to a Kelvin-Helmholtz instability resulting from an inflection point near the canopy top in the flow profile.
We study the mechanism behind Mo-nami, a phenomenon associated with the synchronous waving of marine grass. Linear stability analysis of a mathematical model incorporating grass 
drag as a continuum field has been 
carried out. Our analysis predicts a critical threshold condition for flow instability leading to Mo-nami and associated waving frequency
which compares well with the experimental observations. Further analysis predicts the existence of two distinct modes of instability which we refer as ``Mode 1'' and ``Mode 2''.
%Mode 1 has many characteristics similar to the Kelvin-Helmholtz instability where shear layer formed near grass tip due to grass drag discontinuity plays a critical role. 
%Mode 2 can be interpreted as instability of 
%inviscid flow through a grass bed where shear layer doesn't play an important role. 
The occurrence of these modes for flow instability depends on submergence ratio and the grass 
number density. Asymptotic analysis along with numerical computation in the limit of dense grass bed has been carried out. The analysis reveals that Mode 1 represents flow instability on the 
scale of shear layer which is formed near grass tip due to drag discontinuity near the canopy top, whereas Mode 2 can be understood as instability on the scale of water column. 
For the parameter regime typical of marine grass beds, the two modes merge and are indistinguishable.
